Improving the Image Acquisition Rate \\ of an Atomic Force Microscope \\ Through Sub-sampling and Reconstruction

### 2019-06-28 latex/afm-cs-main.tex
Update on Overleaf.

\maketitle
\begin{abstract}
  Undersampling-based approaches in Atomic Force Microscopy (AFM) aim
  to reduce the time to acquire an image by reducing the number of
  measurements needed while still maintaining image quality. The approach consists of two components: data acquisition and image reconstruction. While the underlying idea is straightforward, practical implementation of a working scheme involves solving a variety of non-trivial problems. In this
  paper, we describe one such hardware implementation and demonstration based on the use of collections of short scans
  known as $\mu$--paths. Using a commercial AFM, we acquire data on a
  grating sample. Reconstructions are made from these data using
  a new variant of basis pursuit, Basis Pursuit with Vertical
  Variation, that is designed to reduce artifacts arising from
  the sampling pattern. The quality of the resulting images is
  compared to images from standard raster scans of the same regions at
  comparable imaging rates using both the peak signal-to-noise ratio
  and the structured similarity index metric and a new metric we call
  the relative damage index. These images are compared (across a range of scan speeds)
  to both standard raster
  scans as well as to simple subline sampling where only a subset of the
  rows of the image are acquired (followed by reconstruction).
  These experiments show that at low sampling densities and slow scan rates,
  $\mu$-path scanning achieves better image quality than subline sampling.
  Conversely, for faster scan rates, subline sampling achieves better image quality
  in less time.
  % These experiments demonstrate that at slow scan
  % rates, the $\mu-$path scheme produces similar image quality with
  % significantly less sampling (and thus less tip-sample interaction)
  % and that at high rates, the undersampling scheme produces higher
  % quality images than raster scanning.
\end{abstract}

@@

\subsection{Comparison to Sub-line Sampling} \label{sec:cp_subline}
Many sub-line sampling papers assume that the lines to sample are
selected randomly \cite{han_optimal_2018, Luo_nano_2015}. An even
simpler alternative to $\mu$-path sampling is simply to take a
standard raster scan with fewer lines. This is the technique we
consider in this subsection, by scanning images with 128 and 64 lines.
For each of these scenarios, we first divide the data for each line
into 512 bins. This gives an image that is 128 (resp., 64) pixels by
512 pixels. We then linearly interpolate along each column to produce
a 512 by 512 pixel image. Again, we take these coarser raster scans at
1.0, 2.5, 5.0, 8.0 and 10.0 Hz. The resulting images are shown in
Fig.~\ref{fig:results_subline_images}.

@@

Fig.~\ref{fig:improve_512} compares the amount of speed improvement of
the different sub-sampling schemes over a full raster scan with 512
lines as a function of scan rate. As far as pure speed goes, the CS
scan at 12.5\% is the fastest for a rate of 1~Hz, though the 64 line
raster scan is close. At the same time, the image quality of the 1~Hz,
12.5\% CS scan is better than the the 1~Hz 64 line raster scan.
However, this advantage quickly evaporates for faster scan rates.
Indeed, for rates beyond about 5~Hz, the raster scan with 128 lines is
not only faster than the 12.5\% CS scan, it also has (arguably) better
image quality, at least on the sample used.

>>>>

\maketitle
\begin{abstract}
  Undersampling-based approaches in Atomic Force Microscopy (AFM) aim
  to reduce the time to acquire an image by reducing the number of
  measurements needed while still maintaining image quality. The approach consists of two components: data acquisition and image reconstruction. While the underlying idea is straightforward, practical implementation of a working scheme involves solving a variety of non-trivial problems. In this
  paper, we describe one such hardware implementation and demonstration based on the use of collections of short scans
  known as $\mu$--paths. Using a commercial AFM, we acquire data on a
  grating sample. Reconstructions are made from these data using
  a new variant of basis pursuit, Basis Pursuit with Vertical
  Variation, that is designed to reduce artifacts arising from
  the sampling pattern. The quality of the resulting images is
  compared to images from standard raster scans of the same regions at
  comparable imaging rates using both the peak signal-to-noise ratio
  and the structured similarity index metric and a new metric we call
  the relative damage index. These images are compared (across a range of scan speeds)
  to both standard raster
  scans as well as to simple subline sampling where only a subset of the
  rows of the image are acquired (followed by reconstruction).
  These experiments show that at low sampling densities and slow scan rates,
  $\mu$-path scanning achieves better image quality than subline sampling.
  Conversely, for faster scan rates, subline sampling achieves better image quality
  in less time, though at a penalty in the damage index.
  % These experiments demonstrate that at slow scan
  % rates, the $\mu-$path scheme produces similar image quality with
  % significantly less sampling (and thus less tip-sample interaction)
  % and that at high rates, the undersampling scheme produces higher
  % quality images than raster scanning.
\end{abstract}

@@

\subsection{Comparison to Sub-line Sampling} \label{sec:cp_subline}
Many sub-line sampling papers assume that the lines to sample are
selected randomly \cite{han_optimal_2018, Luo_nano_2015}. An even
simpler alternative to $\mu$-path sampling is simply to take a
standard raster scan with fewer lines. This is the technique we
consider in this subsection, by scanning images with 128 and 64 lines.
For each of these scenarios, we first divide the data for each line
into 512 bins. This gives an image that is 128 (resp., 64) pixels by
512 pixels, corresponding to 25\% (resp., 12.5\% sampling). We then linearly interpolate along each column to produce
a 512 by 512 pixel image. Again, we take these coarser raster scans at
1.0, 2.5, 5.0, 8.0 and 10.0 Hz. The resulting images are shown in
Fig.~\ref{fig:results_subline_images}.

@@

Fig.~\ref{fig:improve_512} compares the amount of speed improvement of
the different sub-sampling schemes over a full raster scan with 512
lines as a function of scan rate. As far as pure speed goes, the CS
scan at 12.5\% is the fastest for a rate of 1~Hz, though the 64 line
raster scan is close. At the same time, the image quality of the 1~Hz,
12.5\% CS scan is better than the the 1~Hz 64 line raster scan.
However, this advantage quickly evaporates for faster scan rates.
Indeed, for rates beyond about 5~Hz, the raster scan with 128 lines is
not only faster than the 12.5\% CS scan, it also has (arguably) better
image quality, at least on the sample used. However, as seen in Fig.~\ref{fig:time_damage}, the 12.5\% CS scan has better RDI performance that the 128 line scan.
